
Reproducible Research: Peer Assessment 1
========================================

##Loading and preprocessing the data

```{r loading and preprocessing, echo=TRUE}
data <- read.csv('activity.csv')
data$date<-as.Date(data$date,'%Y-%m-%d')
```

##What is mean total number of steps taken per day?

```{r Mean steps, echo=TRUE}
aggDate <- aggregate(steps~date, data, sum)
hist(aggDate$steps, main='Histogram of Total Steps on each day', xlab='Steps per day')
Mean<-round(mean(aggDate$steps), digits=3)
Median<-median(aggDate$steps)
```

Mean total number of steps taken per day is `r Mean`  
Median of total number of steps taken per day is `r Median`

##What is the average daily activity pattern?

```{r daily activity pattern, echo=TRUE}
aggInterval <- aggregate(steps~interval, data, mean)
plot(aggInterval, type='l', xlab='5 Minute Interval')
MaxInterval <- aggInterval$interval[aggInterval$steps==max(aggInterval$steps)]
```
5 minute interval that has the maximum number of steps is `r MaxInterval`

##Imputing missing values

```{r Imputing missing values, echo=TRUE}

NumberofNAs <- sum(is.na(data$steps))
ModifiedData <- data
for(i in 1:nrow(ModifiedData)){
    if(is.na(ModifiedData[i,1])){
        ModifiedData[i,1]<-aggInterval$steps[aggInterval$interval==ModifiedData[i,3]]
    }
}

aggDate_M <- aggregate(steps~date, ModifiedData, sum)
hist(aggDate_M$steps, main='Histogram of Total Steps on each day without NA')
Mean_M<-mean(aggDate_M$steps)
Median_M<-median(aggDate_M$steps)
```
Number of missing values is `r NumberofNAs`  
Mean of number of steps taken per day after inserting missing values is `r Mean_M`  
Median of number of steps taken per day after inserting missing values is `r Median_M`  

##Are there differences in activity patterns between weekdays and weekends?

```{r weekday weekend patterns, echo=TRUE}
library(chron)
ModifiedData[,'Day']<-vector('character')
for(i in 1:nrow(ModifiedData)){
    if(is.weekend(ModifiedData[i,2])){
        ModifiedData[i,4]<-'weekend'
    }else ModifiedData[i,4] <- 'weekday'
}
ModifiedData <- aggregate(steps~interval+Day, ModifiedData, mean)
library(lattice)
xyplot(steps~interval | factor(Day), data=ModifiedData, layout=c(1,2), xlab='interval',ylab='Number of Steps', type='l')
```
